Nested Sampling with Multiple Objective Functions

### 2018-06-05 doc/ms.tex
Fixed derivation

Another feature of NS is that its output can be used to reconstruct
any constrained prior. Consider the Nested Sampling measure, proportional
to the amount of time
NS spends in each region of the space (see \citet{polson2014vertical}
for further discussion of this concept, and a derivation of it from some
desiderata).
Since NS moves at a constant rate
in terms of $\log(X)$, this measure is proportional to
\begin{align}
m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.\label{eqn:measure}
\end{align}
and is improper if we imagine an NS run that does not terminate.
Consider using $m_{NS}$ as an importance sampling-type distribution to
estimate properties of a constrained prior
$p(\xx ; \ell) = \pi(\xx)\mathds{1}(L(\xx) > \ell)/X(\ell)$.
How useful $m_{\rm NS}$ is for determining properties of $p(\xx ; \ell)$
may be indicated by the KL-divergence from the former to the latter:
\begin{align}
D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
    &= \int p(\xx ; \ell)
                \log \left(\frac{p(\xx ; \ell)}{m_{\rm NS}(\xx)}\right)
                \, d\xx \\
    &= \textnormal{const} + \int_{L(\xx) > \ell} \frac{\pi(\xx)}{X(\ell)}
                \log \left(\frac{X(L(\xx))}{X(\ell)}\right) \, d\xx
\end{align}
Rewriting the integral to be with respect to $X$, and taking advantage of the
fact that the implied prior for $X$ is uniform (since $X$ is the complementary
CDF of the likelihood values under $\pi$) gives:
\begin{align}
D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
    &= \textnormal{const} + \int_0^{X(\ell)} \frac{1}{X(\ell)}
                \log \left(\frac{1}{X(\ell)}\right) \, dX
\end{align}

>>>>

Another feature of NS is that its output can be used to reconstruct
any constrained prior. Consider the Nested Sampling measure, proportional
to the amount of time
NS spends in each region of the space (see \citet{polson2014vertical}
for further discussion of this concept, and a derivation of it from some
desiderata).
Since NS moves at a constant rate
in terms of $\log(X)$, this measure is proportional to
\begin{align}
m_{\rm NS} &\propto \frac{\pi(\xx)}{X(L(\xx))}.\label{eqn:measure}
\end{align}
and is improper if we imagine an NS run that does not terminate.
Consider using $m_{NS}$ as an importance sampling-type distribution to
estimate properties of a constrained prior
$p(\xx ; \ell) = \pi(\xx)\mathds{1}(L(\xx) > \ell)/X(\ell)$.
How useful $m_{\rm NS}$ is for determining properties of $p(\xx ; \ell)$
may be indicated by the KL-divergence from the former to the latter:
\begin{align}
D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
    &= \int p(\xx ; \ell)
                \log \left(\frac{p(\xx ; \ell)}{m_{\rm NS}(\xx)}\right)
                \, d\xx \\
    &= \textnormal{const} + \int_{L(\xx) > \ell} \frac{\pi(\xx)}{X(\ell)}
                \log \left(\frac{X(L(\xx))}{X(\ell)}\right) \, d\xx
\end{align}
Rewriting the integral to be with respect to $X$,
and taking advantage of the
fact the implied prior for $X$ is uniform (since $X$ is the complementary
CDF of the likelihood values under $\pi$), gives:
\begin{align}
D_{\rm KL}\left(p(\xx ; \ell) || m_{\rm NS}(\xx)\right)
    &= \textnormal{const} + \frac{1}{X(\ell)}\int_0^{X(\ell)} 
                \log \left(\frac{X}{X(\ell)}\right) \, dX\\
    &= \textnormal{const} + \frac{1}{X(\ell)}\left(
                    X(\ell)\log \left(\frac{X(\ell)}{X(\ell)}\right) - X(\ell)\right)\\
    &= \textnormal{const} -1 = \textnormal{const}'.
\end{align}
